A Logistic Regression Prediction of 2024 Election Odds Gives VP Harris a 38.3% Winrate

### 2024-11-04 paper/paper.qmd
laaaaaast changes

>>>>

Finally, the lack of data regarding the Harris-Trump race, due to Harris starting her presidential race uncharacteristically late, is also a main reason for the limitations of our model.

Potential next steps could be taken to improve the model in the future: more data could be aggregated manually (from pollsters not recorded by FiveThirtyEight), stronger predictor variables that are specifically more correlated with partisanship could be marked and utilised in our model, and individual weightings could be utilised and applied to the data based on each pollster's "track record" with regards to the error, bias, and variance in their previous polls and estimates.
